\documentclass{article}

\title{Facilities, Equipment, and Other Resources}
\date{}

\begin{document}
\maketitle

The primary equipment used in this project will be standard workstations and commodity computing equipment; e.g., for Python library experimentation, high-end workstations or even laptops with GPUs will suffice. Northern Arizona University has the usual high-end network and computing infrastructure for standard computing uses.  Should the need for more ambitious computing requirements arise, Northern Arizona University provides access to powerful additional computing infrastructure, also available to this project.

AEGIS is a private cloud computing facility being developed collaboratively by the University of Arizona (UA), Northern Arizona University, and Arizona State University (ASU) with the support of the Arizona Board of Regents. AEGIS is based on the NSF-supported iPlant (now CyVerse) cyberinfrastructure (http://www.iplantcollaborative.org) ) and provides cloud-based services to researchers and educators in the environmental and ecological sciences. It uses the NSF-supported iRODS (www.irods.org) distributed storage service and the OpenStack open-source cloud operating system, enabling researchers to develop custom images that support scientific workflows and deploy them as virtual machines in to the AEGIS cloud for execution. NAU’s AEGIS hardware platform is networked with servers at UA and ASU and consists of a storage server with 2 X Intel Xeon E5-2620 2.00 GHz 8-core processors, 64 GB of DDR3 ECC memory, and 96 TB of disk storage in a RAID-6 configuration.

NAU’s Monsoon high-performance computing facility is a capacity-type, Linux-based computer cluster with 856 Intel Xeon cores, 12TB of memory, and 4 Nvidia Tesla K80 gpu cores. It has been designed to be flexible and handle a diverse set of research requirements. 31 individual systems are interconnected via FDR Infiniband at a rate of 56Gbps and $<.07$ us latency. Cluster nodes have access to 750TB of shared storage via FDR Infiniband. Monsoon has a measured peak performance of 19 teraflops. It is housed in the NAU ITS Server Co-Location Room, which contains the necessary power and other facilities requirements such as a non- water fire suppression system.

\end{document}
